Online Multiclass Linear Classification with Bandit Feedback

### 2018-11-29 arxiv-version/main.tex
Add a reference
More work on polynomials

\begin{algorithm}[h]
\caption{\textsc{Online Multiclass Classification with Bandit Feedback}
\label{algorithm:game-protocol}}
\begin{algorithmic}[1]
{
\REQUIRE{Number of classes $K$. Number of rounds $T$.}
\FOR{$t=1,2,\dots,T$}
\STATE{Observe feature vector $x_t$}
\STATE{Environment \emph{secretly} chooses correct class label $y_t \in \{1,2,\dots,K\}$}
\STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$}
\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \begin{cases}
0 & \text{if $\widehat y_t = y_t$,} \\
1 & \text{if $\widehat y_t \neq y_t$.}
\end{cases}$
}
\ENDFOR
}
\end{algorithmic}
\end{algorithm}

@@

These algorithms differ by choice of the mapping or, equivalently, choice of the
kernel. The crux of the problem is the analysis of the approximation properties
of these mappings/kernels and the way margin in original space under standard
linear separability notion gets transformed into a margin in the
high-dimensional space under the strong separability notion. This problem is
related to the problem of learning intersection of halfspaces and has been
studied previously by \cite{Klivans-Servedio-2008}.

@@

@@

@@

\section{Converting linear separability to strong linear separability}
\label{section:converting-linear-separability-to-strong-linear-separability}

@@

We construct several different mappings $\phi$. The parameters $R'$ and
$\gamma'$ for the different mappings are not the same, but the ratios
$R'/\gamma'$ are qualitively the same. However, one mapping has the advantage of
having a kernel $k(x,x')$ that is faster to evaluate. Another mapping has the
advantage that one does \emph{not} need to know the initial margin $\gamma$. In
other words, the same mapping works for all possible values of $\gamma > 0$.

The idea behind all the mappings is that, on a compact set, multivariate
polynomials uniformly approximate any continuous function. This result is a
special case of the well known Stone-Weierstrass theorem; see
e.g.~\citep[Section~10.10]{Davidson-Donsig-2010}. In our case, we use
multivariate polynomial to approximate the indicator function corresponding to
the intersection of $K-1$ halfspaces. This polynomial separates examples in one
class from examples in the other classes. To be able to quantify $\gamma'$ and
$R'$ as well as time complexity of evaluating $k(x,x')$ we need to quantify
certain parameters of the approximating polynomial (degree, norm, range of
values). We construct two different polynomials with different paremeters. The
parameters are quantified in
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
stated below.

@@

\begin{lemma}[Inequality]
\label{lemma:inequality}
For any real numbers $b_1, b_2, \dots, b_n$,
$$
\left( \sum_{i=1}^n b_i \right)^2 \le n \sum_{i=1}^n b_i^2 \; .
$$
\end{lemma}

\autoref{lemma:inequality} follows from Cauchy-Schwartz inequality applied to
vectors $(b_1, b_2, \dots, b_n)$ and $(1,1,\dots,1)$.

@@

To prove the first part, we express $p_j$ as
$$
p_j(x) = \sum_{A_j} c^{(j)}_{A_j} x^{A_j} \; .
$$
If $p$ has expansion $p(x) = \sum_A c_A x^A$ then its coefficient $c_A$ for any multi-index $A$ is
$$
c_A = \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \; .
$$
Therefore,
\begin{multline*}
\norm{p}^2
= \sum_{A} (c_A)^2
= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \right)^2
= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
\end{multline*}
and
\begin{multline*}
\prod_{i=1}^n \norm{p_i}^2
= \prod_{i=1}^n \left( \sum_{A_i} (c^{(i)}_{A_i})^2 \right)
= \sum_{(A_1, A_2, \dots, A_n)} \prod_{j=1}^n (c^{(j)}_{A_j})^2
= \sum_{(A_1, A_2, \dots, A_n)} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \\
= \sum_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
\end{multline*}
where in both cases the outer sum is over multi-indices $A$ such that $\norm{A}_1 \le \deg(p)$.
To finish the proof, it is sufficient to prove that for any $A$ such that $\norm{A}_1 \le \deg(p)$,
$$
\left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
\le n^{\deg(p)} \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \; .
$$
This inequality follows from \autoref{lemma:inequality} as long we can show that
the number of $n$-tuples $(A_1, A_2, \dots, A_n)$ such that $A_1 + A_2 + \dots +
A_n = A$ is upper bounded by $n^{\deg(p)}$.

@@

To prove the third part we use generalized triangle inequality and an
\autoref{lemma:inequality}. We have
\begin{align*}
\norm{\sum_{j=1}^n p_j}^2 = \left( \norm{\sum_{j=1}^n p_j} \right)^2 \le \left(\sum_{j=1}^n \norm{p_j} \right)^2 \le n \sum_{j=1}^n \norm{p_j}^2 \; .
\end{align*}
\end{proof}

@@

\begin{proposition}[Properties of Chebyshev polynomials]
\label{proposition:properties-of-chebyshev-polynomials}
Chebyshev polynomials satisfy
\begin{enumerate}
\item $\deg(T_n) = n$ for all $n \ge 0$.
\item If $n \ge 1$, the leading coefficient of $T_n(z)$ is $2^{n-1}$.
\item $|T_n(z)| \le 1$ for all $z \in [-1,1]$ and all $n \ge 0$.
\item $T_n(z) \ge 1 + n^2(z - 1)$ for all $z \ge 1$ and all $n \ge 0$.
\item All coefficients of $T_n(z)$ lie in the interval $\left[-(1+\sqrt{2})^n, (1+\sqrt{2})^n \right]$.
\end{enumerate}
\end{proposition}

\begin{proof}[Proof of \autoref{proposition:properties-of-chebyshev-polynomials}]
The first two proprties easily follow from the recurrence.

The third property is a direct consequence of
\begin{equation}
\label{equation:trigonometric-chebyshev}
T_n(\cos(\theta)) = \cos(n \theta) \qquad \quad \text{for all $\theta \in \R$.}
\end{equation}
since for any $x \in [-1,1]$ there exists $\theta \in \R$ such that $\cos(\theta) = x$.
Equation \eqref{equation:trigonometric-chebyshev} is proved by induction on $n$. Indeed, by definition
$$
T_0(\cos(\theta)) = 1 = \cos(0 \theta) \qquad \text{and} \qquad T_1(\cos(\theta)) = \cos(\theta) \; .
$$
For $n \ge 1$, we have
\begin{align*}
T_{n+1}(\cos(\theta))
& = 2 \cos(\theta) T_n(\cos(\theta)) - T_{n-1}(\cos(\theta)) \\
& = 2 \cos(\theta) \cos(n \theta) - \cos((n-1)\theta)) \; ,
\end{align*}
where the last step follow by induction hypothesis.
It remains to show that the last expression equals $\cos((n+1)\theta)$.
This can be derived from the trigonometric formula
$$
\cos(\alpha \pm \beta) = \cos(\alpha) \cos(\beta) \mp \sin(\alpha) \sin(\beta) \; .
$$
By substituting $\alpha = n \theta$ and $\beta = \theta$, we get two equations
\begin{align*}
\cos((n+1) \theta) & = \cos(n \theta) \cos(\theta) - \sin(n \theta) \sin(\theta) \; , \\
\cos((n-1) \theta) & = \cos(n \theta) \cos(\theta) + \sin(n \theta) \sin(\theta) \; .
\end{align*}
Summing them yields
$$
\cos((n+1)\theta) + \cos((n-1) \theta) = 2 \cos(n \theta) \cos(\theta)
$$
which finishes the proof of equation \eqref{equation:trigonometric-chebyshev}.

To verify the fourth property we first show that
\begin{equation}
\label{equation:hyperbolic-chebyshev}
T_n(\cosh(\theta)) = \cosh(n \theta) \qquad \quad \text{for all $\theta \in \R$.}
\end{equation}
The proof of equation~\eqref{equation:hyperbolic-chebyshev} is the same
as the proof of equation \eqref{equation:trigonometric-chebyshev} except
that we replace $\cos$ and $\sin$ with $\cosh$ and $\sinh$ respectively.

Note that $\cosh(\theta) = \frac{e^{\theta} + e^{-\theta}}{2}$ is an even
continuous function that maps $\R$ onto $[1,+\infty)$, is strictly decreasing
on $(-\infty,0]$, and is strictly increasing on $[0,\infty)$. Thus the fourth
property is equivalent to
$$
T_n(\cosh(\theta)) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$.}
$$
For $\theta = 0$, according to \eqref{equation:hyperbolic-chebyshev} both sides
are equal to $1$. Thus, it is sufficient to prove that the derivative of the
left hand side is greater or equal to the derivative of the right hand side.
That is, we need to prove that
\begin{equation}
\label{equation:hyperbolic-chebyshev-derivative-inequality}
\frac{\diff T_n(\cosh(\theta))}{\diff \theta} \ge \frac{\diff (1 + n^2 (\cosh(\theta) - 1))}{\diff \theta} \qquad \text{for all $\theta \ge 0$.}
\end{equation}
Using \eqref{equation:hyperbolic-chebyshev} and recalling that $\frac{\diff \cosh(\theta)}{\diff \theta} = \sinh(\theta)$ we
can express the derivatives as
\begin{align*}
\frac{\diff T_n(\cosh(\theta))}{\diff \theta} & = \frac{\diff \cosh(n \theta))}{\diff \theta} = n \sinh(n \theta) \; , \\
\frac{\diff (1 + n^2 (\cosh(\theta) - 1))}{\diff \theta} & = n^2 \sinh(\theta) \; .
\end{align*}
The inequality \eqref{equation:hyperbolic-chebyshev-derivative-inequality} is thus equivalent to
$$
\sinh(n \theta) \ge n \sinh(\theta) \qquad \text{for all $\theta \ge 0$.}
$$
Tho prove this inequality we use the summation formula
$$
\sinh(\alpha + \beta) = \sinh(\alpha) \cosh(\beta) + \sinh(\beta) \cosh(\beta)
$$
and the observation that for $\theta \ge 0$, $\cosh(\theta) \ge 1$ and $\sinh(\theta) \ge 0$. Thus,
$$
\sinh(\alpha + \beta) \ge \sinh(\alpha) + \sinh(\beta) \qquad \text{for $\alpha, \beta \ge 0$.}
$$
Thus by induction on $n$, we see that $\sinh(n \theta) \ge n \sinh(\theta)$ for all $\theta \ge 0$.

To verify the fifth property let $a_n$ be the magnitude of the largest
coefficient of $T_n(z)$. The recurrence for Chebyshev polynomials
implies that the sequence $a_0, a_1, a_2, \dots$ satisfies
\begin{align*}
a_0 & = a_1 = 1 \; , \\
a_{n+1} & \le 2 a_n + a_{n-1} & \text{for $n \ge 1$.}
\end{align*}
It remains to show that $a_n \le (1 + \sqrt{2})^n$ for all $n \ge 0$. We do this
by induction on $n$. For $n=0$ and $n=1$ the inequality trivially holds. For $n
\ge 1$, we have
\begin{align*}
a_{n+1} \le 2 a_n + a_{n-1}
& \le 2 (1 + \sqrt{2})^n + (1 + \sqrt{2})^{n-1} \\
& = (1 + \sqrt{2})^{n-1} (2 (1 + \sqrt{2}) + 1) \\
& = (1 + \sqrt{2})^{n-1} (3 + 2\sqrt{2}) \\
& = (1 + \sqrt{2})^{n-1} (1 + \sqrt{2})^2 \\
& = (1 + \sqrt{2})^{n+1} \; .
\end{align*}

>>>>

\begin{algorithm}[h]
\caption{\textsc{Online Multiclass Classification with Bandit Feedback}
\label{algorithm:game-protocol}}
\begin{algorithmic}[1]
{
\REQUIRE{Number of classes $K$. Number of rounds $T$.}
\FOR{$t=1,2,\dots,T$}
\STATE{Observe feature vector $x_t$}
\STATE{Adversary \emph{secretly} chooses correct class label $y_t \in \{1,2,\dots,K\}$}
\STATE{Predict class label $\widehat y_t \in \{1,2,\dots,K\}$}
\STATE{Observe feedback $z_t \in \{0,1\}$ where $z_t = \begin{cases}
0 & \text{if $\widehat y_t = y_t$,} \\
1 & \text{if $\widehat y_t \neq y_t$.}
\end{cases}$
}
\ENDFOR
}
\end{algorithmic}
\end{algorithm}

@@

These algorithms differ by choice of the mapping or, equivalently, choice of the
kernel. The crux of the problem is the analysis of the approximation properties
of these mappings/kernels and the way margin in original space under standard
linear separability notion gets transformed into a margin in the
high-dimensional space under the strong separability notion. This problem is
related to the problem of learning intersection of halfspaces and has been
studied previously by \cite{Klivans-Servedio-2008}. As an important technical
achievement, we improve on the results of \cite{Klivans-Servedio-2008} by
removing completely the dependency on the original dimension $d$.

@@

\item \cite{Chen-Chen-Zhang-Chen-Zhang-2009}

@@

\item \cite{Foster-Kale-Luo-Mohri-Sridharan-2018}

@@

\section{From linear separability to strong linear separability}
\label{section:from-linear-separability-to-strong-linear-separability}

@@

We construct several different mappings $\phi$. The mappings differ in the
parameters $R'$, $\gamma'$, time complexity of evaluating $\phi(x)$, and time
complexity of evaluating $k(x,x')$. Some of the mappings depend the original
margin $\gamma$. In practice, the margin parameter $\gamma$ is not known, which
makes these mappings impractical. However, one of the mappings we construct
does \emph{not} depend $\gamma$.

The idea behind all the mappings is polynomial approximation. According to the
well known Stone-Weierstrass theorem (see
e.g.~\citep[Section~10.10]{Davidson-Donsig-2010}), on a compact set,
multivariate polynomials uniformly approximate any continuous function. In our
case, we use multivariate polynomial to approximate the indicator function
corresponding to the intersection of $K-1$ halfspaces. This polynomial separates
examples in one class from examples in the other classes. To be able to quantify
$R'$, $\gamma'$ and time complexities of evaluating $\phi(x)$ and $k(x,x')$, we
need to quantify certain parameters of the approximating polynomial (degree,
norm). We construct two different polynomials with different paremeters. The
parameters are quantified in
Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}
stated below.

@@

\section{Proof of Theorems~\ref{theorem:polynomial-approximation-1}~and~\ref{theorem:polynomial-approximation-2}}

For the proofs of the theorems we need several auxilliary results.

\begin{lemma}[Simple inequality]
\label{lemma:simple-inequality}
For any real numbers $b_1, b_2, \dots, b_n$,
$$
\left( \sum_{i=1}^n b_i \right)^2 \le n \sum_{i=1}^n b_i^2 \; .
$$
\end{lemma}

\begin{proof}
The lemma follows from Cauchy-Schwartz inequality applied to
vectors $(b_1, b_2, \dots, b_n)$ and $(1,1,\dots,1)$.
\end{proof}

\begin{lemma}[Bound on binomial coefficients]
\label{lemma:binomial-bound}
For any integers $n,k$ such that $n \ge k \ge 0$,
$$
\binom{n}{k} \le (n - k + 1)^k \; .
$$
\end{lemma}

\begin{proof}
If $k = 0$, the inequality trivially holds. For the rest of the proof we can
assume $k \ge 1$. We write the binomial coefficient as
$$
\binom{n}{k} = \frac{n(n-1)\cdots(n-k+1)}{k(k-1) \cdots 1} = \frac{n}{k} \cdot \frac{n-1}{k - 1} \cdots \frac{n-k+1}{1} \; .
$$
We claim that
$$
\frac{n}{k} \le \frac{n-1}{k - 1} \le \cdots \le \frac{n-k+1}{1}
$$
from which the lemma follows by upper bounding all the fractions by $n-k+1$.
It remains to prove that for any $j=0,1,\dots,k-1$,
$$
\frac{n - j + 1}{k - j + 1} \le \frac{n - j}{k - j} \; .
$$
Mutliplying by the (positive) denonimators, we get an equivalent inequality
$$
(n - j + 1)(k - j) \le (n - j)(k - j + 1) \; .
$$
Cancelling common terms leads to an equivalent inequality
$$
k - j \le n - j \; ,
$$
which holds by the assumption on $n \ge k$.
\end{proof}

@@

To prove the first part, we express $p_j$ as
$$
p_j(x) = \sum_{A_j} c^{(j)}_{A_j} x^{A_j} \; .
$$
If $p$ has expansion $p(x) = \sum_A c_A x^A$ then its coefficient $c_A$ for any multi-index $A$ is
$$
c_A = \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \; .
$$
Therefore,
\begin{multline*}
\norm{p}^2
= \sum_{A} (c_A)^2
= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} c^{(1)}_{A_1} c^{(2)}_{A_2} \cdots c^{(n)}_{A_n} \right)^2
= \sum_{A} \left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
\end{multline*}
and
\begin{multline*}
\prod_{i=1}^n \norm{p_i}^2
= \prod_{i=1}^n \left( \sum_{A_i} (c^{(i)}_{A_i})^2 \right)
= \sum_{(A_1, A_2, \dots, A_n)} \prod_{j=1}^n (c^{(j)}_{A_j})^2
= \sum_{(A_1, A_2, \dots, A_n)} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \\
= \sum_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
\end{multline*}
where in both cases the outer sum is over multi-indices $A$ such that $\norm{A}_1 \le \deg(p)$.
\autoref{lemma:simple-inequality} implies that for any multi-index $A$,
$$
\left( \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \prod_{j=1}^n c^{(j)}_{A_j} \right)^2
\le M_A \sum_{\substack{(A_1, A_2, \dots, A_n) \\ A_1 + A_2 + \dots + A_n = A}} \left( \prod_{j=1}^n c^{(j)}_{A_j} \right)^2 \; .
$$
where $M_A$ is the number of $n$-tuples $(A_1, A_2, \dots, A_n)$ such that $A_1 +
A_2 + \dots + A_n = A$.

To finish the proof, it is sufficient to prove that
$M_A \le n^{\deg(p)}$. To prove this inequality, consider a multi-index
$A = (i_1, i_2, \dots, i_d)$ and consider its $\ell$-th coordinate $i_\ell$.
In order for $A_1 + A_2 + \dots + A_n = A$, the $\ell$-th coordinates of
$A_1, A_2, \dots, A_n$ need to sum to $i_\ell$. There are exactly $\binom{i_\ell + n - 1}{i_\ell}$
possibilities for the choice of $\ell$-th coordinates of $A_1, A_2, \dots, A_n$.
The total number of choices is thus
$$
M_A = \prod_{\ell=1}^d \binom{i_\ell + n - 1}{i_\ell} \; .
$$
Using \autoref{lemma:binomial-bound}, we upper bound it as
$$
M_A \le \prod_{\ell=1}^d n^{i_\ell} = n^{\norm{A}_1} \le n^{\deg(p)} \; .
$$

@@

To prove the third part we use generalized triangle inequality and
\autoref{lemma:simple-inequality}. We have
\begin{align*}
\norm{\sum_{j=1}^n p_j}^2 = \left( \norm{\sum_{j=1}^n p_j} \right)^2 \le \left(\sum_{j=1}^n \norm{p_j} \right)^2 \le n \sum_{j=1}^n \norm{p_j}^2 \; .
\end{align*}
\end{proof}

@@

\begin{proposition}[Properties of Chebyshev polynomials]
\label{proposition:properties-of-chebyshev-polynomials}
Chebyshev polynomials satisfy
\begin{enumerate}
\item $\deg(T_n) = n$ for all $n \ge 0$.
\item If $n \ge 1$, the leading coefficient of $T_n(z)$ is $2^{n-1}$.
\item $T_n(\cos(\theta)) = \cos(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
\item $T_n(\cosh(\theta)) = \cosh(n \theta)$ for all $\theta \in \R$ and all $n \ge 0$.
\item $|T_n(z)| \le 1$ for all $z \in [-1,1]$ and all $n \ge 0$.
\item $T_n(z) \ge 1 + n^2(z - 1)$ for all $z \ge 1$ and all $n \ge 0$.
\item All coefficients of $T_n(z)$ lie in the interval $\left[-(1+\sqrt{2})^n, (1+\sqrt{2})^n \right]$.
\end{enumerate}
\end{proposition}

\begin{proof}[Proof of \autoref{proposition:properties-of-chebyshev-polynomials}]
The first two properties can be easily proven by induction on $n$ using the recurrence.

We prove third property by induction on $n$. Indeed, by definition
$$
T_0(\cos(\theta)) = 1 = \cos(0 \theta) \qquad \text{and} \qquad T_1(\cos(\theta)) = \cos(\theta) \; .
$$
For $n \ge 1$, we have
\begin{align*}
T_{n+1}(\cos(\theta))
& = 2 \cos(\theta) T_n(\cos(\theta)) - T_{n-1}(\cos(\theta)) \\
& = 2 \cos(\theta) \cos(n \theta) - \cos((n-1)\theta)) \; ,
\end{align*}
where the last step follow by induction hypothesis.
It remains to show that the last expression equals $\cos((n+1)\theta)$.
This can be derived from the trigonometric formula
$$
\cos(\alpha \pm \beta) = \cos(\alpha) \cos(\beta) \mp \sin(\alpha) \sin(\beta) \; .
$$
By substituting $\alpha = n \theta$ and $\beta = \theta$, we get two equations
\begin{align*}
\cos((n+1) \theta) & = \cos(n \theta) \cos(\theta) - \sin(n \theta) \sin(\theta) \; , \\
\cos((n-1) \theta) & = \cos(n \theta) \cos(\theta) + \sin(n \theta) \sin(\theta) \; .
\end{align*}
Summing them yields
$$
\cos((n+1)\theta) + \cos((n-1) \theta) = 2 \cos(n \theta) \cos(\theta)
$$
which finishes the proof.

Fourth property has the similar proof as third property. It suffices
to replace $\cos$ and $\sin$ with $\cosh$ and $\sinh$ respectively.

Fifth property follows from the third property. Indeed, for any $z \in [-1,1]$
there exists $\theta \in \R$ such that $\cos \theta = z$. Thus, $|T_n(z)| =
|T_n(\cos(\theta))| = |\cos(n\theta)| \le 1$.

The sixth property is equivalent to
$$
T_n(\cosh(\theta)) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$,}
$$
since $\cosh(\theta) = \frac{e^{\theta} + e^{-\theta}}{2}$ is an even continuous
function that maps $\R$ onto $[1,+\infty)$, is strictly decreasing on
$(-\infty,0]$, and is strictly increasing on $[0,\infty)$. Using the fourth
property the last inequality is equivalent to
$$
\cosh(n \theta) \ge 1 + n^2 (\cosh(\theta) - 1) \qquad \text{for all $\theta \ge 0$.}
$$
For $\theta = 0$, both sides are equal to $1$. Thus, it is sufficient to prove
that the derivative of the left hand side is greater or equal to the derivative
of the right hand side. Recalling that $[\cosh(\theta)]' = \sinh(\theta)$, this
means that we need to show that
$$
\sinh(n \theta) \ge n \sinh(\theta) \qquad \text{for all $\theta \ge 0$.}
$$
Tho prove this inequality we use the summation formula
$$
\sinh(\alpha + \beta) = \sinh(\alpha) \cosh(\beta) + \sinh(\beta) \cosh(\beta) \; .
$$
If $\alpha, \beta$ are non-negative then $\sinh(\alpha), \sinh(\beta)$ are
non-negative and $\cosh(\alpha), \cosh(\beta) \ge 1$. Hence,
$$
\sinh(\alpha + \beta) \ge \sinh(\alpha) + \sinh(\beta) \qquad \text{for any $\alpha, \beta \ge 0$.}
$$
This implies that (using induction on $n$) that $\sinh(n \theta) \ge n
\sinh(\theta)$ for all $\theta \ge 0$.

To verify the seventh property let $a_n$ be the magnitude of the largest
coefficient of $T_n(z)$. The recurrence for Chebyshev polynomials implies that
the sequence $a_0, a_1, a_2, \dots$ satisfies
\begin{align*}
a_0 & = a_1 = 1 \; , \\
a_{n+1} & \le 2 a_n + a_{n-1} & \text{for $n \ge 1$.}
\end{align*}
It remains to show that $a_n \le (1 + \sqrt{2})^n$ for all $n \ge 0$. We do this
by induction on $n$. For $n=0$ and $n=1$ the inequality trivially holds. For $n
\ge 1$, we have
\begin{align*}
a_{n+1} \le 2 a_n + a_{n-1}
& \le 2 (1 + \sqrt{2})^n + (1 + \sqrt{2})^{n-1} \\
& = (1 + \sqrt{2})^{n-1} (2 (1 + \sqrt{2}) + 1) \\
& = (1 + \sqrt{2})^{n-1} (3 + 2\sqrt{2}) \\
& = (1 + \sqrt{2})^{n-1} (1 + \sqrt{2})^2 \\
& = (1 + \sqrt{2})^{n+1} \; .
\end{align*}
